\papertitle

### 2013-01-29 manuscript.tex
new item class for list with custom bullets

@@

We validate our system model experimentally by systematically attempting to
guide the H$^2$Bird through the window using the directed headings from the
ground station at various starting initial conditions. We compare the results of the
experiments to the computed backwards reachable set of feasible initial
conditions and a Monte Carlo simulation to determine the accuracy of our system 
model.

@@

Each trial included the following steps (see Fig.~\ref{fig:pf_screencap}):
\begin{enumerate}
\item We identify the window to the ground station by dragging a bounding 
box over it using a mouse. 
\item We release H$^2$Bird by hand, in view of the camera at the desired 
starting grid point.
\item The H$^2$Bird attempts to fly through the window, with remote 
guidance from the ground station.
\end{enumerate}

>>>>

% descriptor list for storyboard figure
\newenvironment{spaced_description}[1]
  {\begin{list}{}%
   {\renewcommand\makelabel[1]{##1:\hfill}%
   \settowidth\labelwidth{\makelabel{#1}}%
   \setlength\leftmargin{\labelwidth}
   \addtolength\leftmargin{\labelsep}}}
  {\end{list}}

@@

We validate our system model experimentally by systematically guiding the
H$^2$Bird through the window at various starting initial conditions. We
compare the results of the experiments to the computed backwards reachable set
of feasible initial conditions and a Monte Carlo simulation to determine the
accuracy of our system model.

@@

Each trial included the following steps (see Fig.~\ref{fig:pf_screencap}):
\begin{spaced_description}{\textbf{(4-6)}}
\item[\textbf{(1,2)}] We identify the window to the ground station by dragging a bounding 
box over it using a mouse. 
\item[\textbf{(3)}] We release H$^2$Bird by hand, in view of the camera at the desired 
starting grid point.
\item[\textbf{(4-6)}] The H$^2$Bird attempts to fly through the window, with remote 
guidance from the ground station.
\end{spaced_description}
